Untitled Draft

### 2023-03-14 doc/manuscript.Rmd
Fix tag for table 1
Prepare to apply tabulation to other outcomes.

\renewcommand{\arraystretch}{0.8}

```{r sleep-by-exercise}
note <- "Adjusted for SES, BMI, and sex. "

format_table <- function(tab){
  tab$term <- gsub("I\\(","", tab$term) |> 
    gsub("_", " ", x = _) |> 
    gsub("\\^2\\)","$^2$", x = _)
  tab
}

@@

sleep_outcomes <- lapply(model_list[sleep_names], function(x){
tab <- format_table(x$table)  
# Remove BMI, sex and ses from table
tab <- tab[!grepl("^ses", tab$term),]
tab <- tab[!grepl("^sex", tab$term),]
tab <- tab[!grepl("^bmi", tab$term),]
tab$term <- gsub("\\bpa\\b", " PA ", tab$term)
tab$term <- stringr::str_to_sentence(tab$term)
names(tab) <- c("Term", "$\\beta$ [95\\% CI]", "SE", "t", "p")
tab
})
names(sleep_outcomes) <- gsub("scale_", "", names(sleep_outcomes)) |> 
  gsub("\\sby.*", "", x = _ ) |> 
  gsub("_", " ", x = _ ) |> 
  stringr::str_to_sentence()

  papaja::apa_table(sleep_outcomes,
                    caption = "Sleep on physical activity volume controlling for SES, gender and BMI",
                    note = note,
                    escape = FALSE)
```

>>>>

\renewcommand{\arraystretch}{0.7}

```{r sleep-by-volume}
note <- "Adjusted for SES, BMI, and sex. "

format_table <- function(tab) {
  tab$term <- gsub("I\\(", "", tab$term) |>
    gsub("_", " ", x = _) |>
    gsub("\\^2\\)", "$^2$", x = _ )
  tab <- tab[!grepl("^ses", tab$term), ]
  tab <- tab[!grepl("^sex", tab$term), ]
  tab <- tab[!grepl("^bmi", tab$term), ]
  tab$term <- gsub("\\bpa\\b", " PA ", tab$term)
  tab$term <- stringr::str_to_sentence(tab$term)
  names(tab) <- c("Term", "$\\beta$ [95\\% CI]", "SE", "t", "p")
  tab
}

@@

sleep_outcomes_by_PA <- lapply(model_list[sleep_names], function(x){
tab <- format_table(x$table)  
tab
})

names(sleep_outcomes_by_PA) <- gsub("scale_", "", names(sleep_outcomes_by_PA)) |> 
  gsub("\\sby.*", "", x = _ ) |> 
  gsub("_", " ", x = _ ) |> 
  stringr::str_to_sentence()

  papaja::apa_table(sleep_outcomes_by_PA,
                    caption = "Sleep on physical activity volume controlling for SES, gender and BMI",
                    note = note,
                    escape = FALSE)
```
